---
title: "Quarto HTML Exercise"
format: html
---
```{r}
#| label: setup
#| echo: false
#| eval: true
#| message: false
library(tidyverse)
library(flextable)
```

::: {.callout-note}
You can click Preview in the upper left corner of the Editor window at any time.
If you save the file after making changes and refresh your browser, you'll see the changes.
:::

1. Create a new R project in Positron. Put it in a folder called "TryQuarto".

::: {.callout-tip title="Hint" collapse="true"}
File -> New Folder from Template
:::

2. Add a new .qmd document called "Theoph.qmd"
3. Using markdown, annotate your code with these level 2 headings: Analysis, Plot
4. Before the Analysis section, insert an R code chunk to load the *tidyverse* metalibrary and *flextable* library. Install these packages using `install.packages()` if you don't have them already. Use the code chunk options to hide the code and messages from the output.

::: {.callout-tip title="Hint" collapse="true"}
```text
#| label: setup
#| echo: false
#| eval: true
#| message: false
```
:::

5. In the analysis section, explain in markdown that you are going to first create a new data frame from `Theoph` called `trough`.
6. Insert an R code chunk. In it use a *tidyverse* pipe if you can, to create `trough`. Label it "create-trough".

::: {.callout-tip title="Hint" collapse="true"}

* `#| label: create-trough`
* Use `dplyr::group_by` to group by `Subject`
* Create new variables with `dplyr::summarize` where *wt* and *dose* are the first records for *Wt* and *Dose*, *time* is the maximum of *Time*, and *conc* is the concentration which occurs at *time*.
* Create new variables with `dplyr::mutate` where *id* is the numeric form of the character form of `Theoph$Subject` and *dosekg* is dose/wt.
* Remove the grouping with `dplyr::ungroup`.
* Use `dplyr::arrange` to sort by *id*

:::

```{r}
#| eval: false
#| code-fold: true
#| code-summary: "Click to reveal an answer"

trough <- 
  Theoph |> 
  group_by(Subject) |>
  summarize(
    wt = Wt[1],
    dose = Dose[1],
    time = max(Time),
    conc = conc[which(Time == time)]
  ) |>
  mutate(
    id = as.numeric(as.character(Subject)),
    dosekg = dose / wt
  ) |>
  ungroup() |>
  arrange(id)
```

    
7. What happens if you add `#| echo: false` or `#| eval: false` to the code chunk?
8. Add markdown to indicate you are examining how well dose predicts trough.
8. In the next R chunk labeled "dose-lm" with echoing and evaluation, use the `stats::lm` function to create a linear regression called `lm_dose` of `trough$dose` as a predictor of `trough$conc`. Include a summary of `lm_dose` in your code chunk.

::: {.callout-tip title="Hint" collapse="true"}

- `?lm`
- `lm_dose <- lm(...)`

:::

```{r}
#| eval: false
#| code-fold: true
#| code-summary: "Click to reveal the answer"

lm_dose <- lm(conc ~ dose, data = trough)
summary(lm_dose)
```

9. Add more markdown to indicate you are now going to check if *dosekg* is a better predictor of the trough concentration.  **Bold** important parts of your text.
10. Add another R chunk with **no** echoing labeled "dosekg-lm"  to create a linear regression called `lm_dosekg` of `trough$dosekg` as a predictor of `trough$conc`.
11. Add an R chunk with both echo and evaluation to summarize `lm_dosekg`.
12. After the level 2 "Plot" heading, visualize both regressions with `ggplot`, `geom_point`, and `geom_smooth`.

::: {.callout-tip title="Hint" collapse="true"}

`trough |> ggplot(aes( x = ? , y = ?)) + geom_point() + geom_smooth(method = "lm")`

:::

```{r}
#| eval: false
#| code-fold: true
#| code-summary: "Click to reveal the answer"

trough |> ggplot(aes( x = dose, y = conc)) + geom_point() + geom_smooth(method = "lm")

```

13. Write a conclusion in markdown after another level 2 heading.
14. Find `Quarto: Render Document` in the Command Palette and click it. This will render your document to HTML. You can also use the keyboard shortcut `Ctrl + Shift + K` (Windows) or `Cmd + Shift + K` (Mac).



